---
title: "remap_nofafsa_dialing_task_ug_analysis"
output: html_document
---

# Load libraries
```{r load-libraries, include=FALSE}
# setup
library(DBI)
library(odbc)
library(tidyverse)
library(gt)
library(dplyr)
library(snhuthemes)
library(tidymodels)
library(lubridate)
library(airtabler)
library(ggtext)
library(calendR)

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center',
  fig.width = 10,
  fig.height = 6
)
```


#database connection
```{r connection-string,include=FALSE}
#database connection
con_data_reporting <- dbConnect(odbc::odbc(), .connection_string = "Driver={SQL Server Native Client 11.0};\n                          Server=COCE-DS-LSTNR,50222;\n                          Database=Data_Reporting;\n                          trusted_connection=yes;")
```




#import data from query (old query, don't use)
```{r}
nofafsa_df <- dbGetQuery(
  conn = con_data_reporting,
  statement = read_file(
    file = here::here("sql","no_fafsa_dialer_task_ug_21EW4.sql")
  )
) %>% as_tibble()
```



#import data from query - REPOPPED
```{r}
nofafsa_df_repop <- dbGetQuery(
  conn = con_data_reporting, 
  statement = read_file(
    file = here::here("sql","no_fafsa_dialer_task_ug_21EW4_repop_2.sql")
  )
) %>% as_tibble()
```



#import fafsa and file complete dates (for weekly complete chart, didn't end up using)
```{r}
fafsa_dates_df <- dbGetQuery(
  conn = con_data_reporting, 
  statement = read_file(
    file = here::here("sql","FAFSA Dates.sql")
  )
) %>% as_tibble()
```


#database connection 50333
```{r connection-string,include=FALSE}
#database connection
con_aardw <- dbConnect(odbc::odbc(), .connection_string = "Driver={SQL Server Native Client 11.0};\n                          Server=COCE-LSTNR,50333;\n                          Database=AARDW;\n                          trusted_connection=yes;")
```



#importing Unify IDs from call logs if they were dialed in no fafsa dialer (used to check if actually dialed, don't need for results)
```{r}
call_logs <- dbGetQuery(
  conn = con_aardw, 
  statement = read_file(
    file = here::here("sql","call_logs.sql")
  )
) %>% as_tibble()
```

#importing melt
```{r}
melt_df <- dbGetQuery(
  conn = con_aardw, 
  statement = read_file(
    file = here::here("sql","melt.sql")
  )
) %>% as_tibble()
```


# joining call logs to 50222 data (used to check if actually dialed, don't need for results)
```{r}
nofafsa_df_calls <-
  as_tibble() %>%
  left_join(x = nofafsa_df,
          y = call_logs,
          by = c("ContactID" = "UnifySalesforceContactID")) 
#%>% 
  #filter(UnifySalesforceContactID != "Unknown")
  
```


# joining melt to 50222 data
```{r}
nofafsa_df_repop_melt <-
  as_tibble() %>%
  left_join(x = nofafsa_df_repop,
          y = melt_df,
          by = c("colleague_id" = "StudentColleagueID")) 
#%>% 
  #filter(UnifySalesforceContactID != "Unknown")
  
```

```{r}
write.csv(nofafsa_df_repop_melt, "C:\\Users\\k.west2\\Desktop\\nofafsa_melt.csv", row.names = FALSE)
```

#import dates table  (for weekly complete chart, didn't end up using)
```{r}
dates_df <- dbGetQuery(
  conn = con_aardw, 
  statement = read_file(
    file = here::here("sql","dates.sql")
  )
) %>% as_tibble()
```


#join to date table - FAFSA File Date (for weekly complete chart, didn't end up using)
```{r}
fafsa_weekly_file_df <-
  as_tibble() %>%
  inner_join(x = fafsa_dates_df,
            y = dates_df,
            by = c("StudentFAFSAFileDate" = "DateFull")) 
```



#join to no fafsa results (for weekly complete chart, didn't end up using)
```{r}
no_fafsa_weekly_file_df <-
  as_tibble() %>%
  left_join(x = fafsa_weekly_file_df,
            y = nofafsa_df_calls,
            by = c("ContactId" = "ContactID")) 
```

```{r}
write.csv(nofafsa_df_calls, "C:\\Users\\k.west2\\Desktop\\ug_dialer_min3.csv", row.names = FALSE)
```

#using original test population assignments with call and task data - this was used to check that test pop was actually dialed (dont need for results)
```{r}
nofafsa_results <- 
  nofafsa_df_calls %>% 
  #filter(fafsa_completed==0) %>% 
  group_by(testing_group) %>% 
  summarise(
      InPopulation = n(), 
      `Funding Tasks` = sum(funding_task),
      `Funding %` = sum(funding_task)/n(),
      `Dialer Tasks` = sum(dialer_task),
      `Dialer Task %` = sum(dialer_task)/n(),
      Dialed = sum(dialed, na.rm=T),
      `Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Test Group` = testing_group) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       `Dialer Task %`,
       `Funding %`,
       `Dialed %`,
      `FAFSA Completion Rate`,
      `Reg Rate`,
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    `Funding Tasks`,
    `Dialer Tasks`,
    Dialed,
     #Apps
     `FAFSA Completed`,
    Regs,
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control")) %>%
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/23/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_results
  
```



#original test results - use for results summary (no call data)
```{r}
nofafsa_results <- 
  nofafsa_df_repop %>% 
  #filter(!is.na(treatment)) %>% 
  group_by(org_testing_group) %>% 
  summarise(
      InPopulation = n(), 
      #`Funding Tasks` = sum(funding_task),
      #`Funding %` = sum(funding_task)/n(),
      #`Dialer Tasks` = sum(dialer_task),
      #`Dialer Task %` = sum(dialer_task)/n(),
      #Dialed = sum(dialed, na.rm=T),
      #`Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Test Group` = org_testing_group) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       #`Dialer Task %`,
       #`Funding %`,
       #`Dialed %`,
      `FAFSA Completion Rate`,
      `Reg Rate`,
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    #`Funding Tasks`,
    #`Dialer Tasks`,
    #Dialed,
     #Apps
     `FAFSA Completed`,
    Regs,
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control"),
    subtitle = md("Original Testing Groups")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/24/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_results 
  
```


```{r}
# Overall results save
nofafsa_results %>% gtsave(filename = "nofafsa_21EW4_overall_20210324_orgpop.png", path = here::here("imgs"))
```


#repopped results
```{r}
nofafsa_repop_results <- 
  nofafsa_df_repop_melt %>% 
  filter(!is.na(treatment)) %>% 
  group_by(treatment, new_test_or_control) %>% 
  summarise(
      InPopulation = n(), 
      #`Funding Tasks` = sum(funding_task),
      #`Funding %` = sum(funding_task)/n(),
      #`Dialer Tasks` = sum(dialer_task),
      #`Dialer Task %` = sum(dialer_task)/n(),
      #Dialed = sum(dialed, na.rm=T),
      #`Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n()
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Treatment` = new_test_or_control) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       #`Dialer Task %`,
       #`Funding %`,
       #`Dialed %`,
      `FAFSA Completion Rate`,
      `Reg Rate`
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    #`Funding Tasks`,
    #`Dialer Tasks`,
    #Dialed,
     #Apps
     `FAFSA Completed`,
    Regs
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control"),
    subtitle = md("Reassigned Testing Groups")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/24/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_repop_results 
  
```


```{r}
# Overall results save
nofafsa_repop_results %>% gtsave(filename = "nofafsa_21EW4_overall_20210324_repop.png", path = here::here("imgs"))
```



#repopped, melt, regs only
```{r}
nofafsa_repop_results_melt <- 
  nofafsa_df_repop_melt %>% 
  filter(!is.na(treatment), Regs == 1, !is.na(EnrolledDay1)) %>% 
  group_by(treatment, new_test_or_control) %>% 
  summarise(
      InPopulation = n(), 
      #`Funding Tasks` = sum(funding_task),
      #`Funding %` = sum(funding_task)/n(),
      #`Dialer Tasks` = sum(dialer_task),
      #`Dialer Task %` = sum(dialer_task)/n(),
      #Dialed = sum(dialed, na.rm=T),
      #`Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
      `Post Start Melts` = sum(EnrolledDay1)-sum(EnrolledDay15),
      `Post Start Melt Rate` = 1-sum(EnrolledDay15)/sum(EnrolledDay1),
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Treatment` = new_test_or_control) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       #`Dialer Task %`,
       #`Funding %`,
       #`Dialed %`,
      `FAFSA Completion Rate`,
      `Post Start Melt Rate`
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    #`Funding Tasks`,
    #`Dialer Tasks`,
    #Dialed,
     #Apps
     `FAFSA Completed`,
    `Post Start Melts`
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control"),
    subtitle = md("Melt Rate - Registered Students")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/24/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_repop_results_melt
  
```
```{r}
# Overall results save
nofafsa_repop_results_melt %>% gtsave(filename = "nofafsa_21EW4_melt_20210324_repop.png", path = here::here("imgs"))
```






#calendars!!!
#create vector of NAs the same length of the calendar I want to make
```{r}
events <- rep(NA,59)
```


#assign events by day in the vector of NAs
```{r}
events[c(21, 35)] <- "Dialer"
events[c(28, 42)] <- "Funding Task"

events


```
#make a pretty calendar
```{r}
treatment_cal <-
  calendR(
   start_date = "2021-01-01",
         end_date = "2021-02-28",
        #year = 2021, month = 1,
        special.days = events,
        special.col = c("lightblue", "lightgreen"),
        low.col = "white",
        days.col = "black",
        bg.col = "white",
        months.col = "black",
        title = NULL,
   mbg.col = "#8eb6de",
        legend.pos = "bottom",
        legend.title = "")

treatment_cal

```


```{r}

ggsave(filename = here::here("imgs","treatment_cal.png"),
       plot = treatment_cal,
       width = 6,
       height = 4)


```






#calendar
```{r}
calendR(year = 2021, month = 1,
        text = c("Dialer", "Funding Task"),
        text.pos = c(21, 28),
        text.size = 3,
        text.col = 4)
```








#working- weekly file complete results
```{r}
fafsa_weekly_file_results <- 
  no_fafsa_weekly_file_df %>% 
  filter(is.na(fafsa_completed)) %>% 
  group_by(WeekStartDate) %>% 
  summarise(
      InPopulation = n(), 
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       Enrolls = sum(Enrolls),
      `Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  #rename(`Test Group` = testing_group) %>% 
 gt() %>%
     fmt_percent(columns = vars(
      `FAFSA Completion Rate`,
      `Reg Rate`,
      `Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
     #Apps
     `FAFSA Completed`,
    Regs,
    Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/1/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


fafsa_weekly_file_results
  
```





