---
title: "remap_nofafsa_dialing_task_ug_analysis"
output: html_document
---

# Load libraries
```{r load-libraries, include=FALSE}
# setup
library(DBI)
library(odbc)
library(tidyverse)
library(gt)
library(dplyr)
library(snhuthemes)
library(tidymodels)
library(lubridate)
library(airtabler)
library(ggtext)

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = 'center',
  fig.width = 10,
  fig.height = 6
)
```


#database connection
```{r connection-string,include=FALSE}
#database connection
con_data_reporting <- dbConnect(odbc::odbc(), .connection_string = "Driver={SQL Server Native Client 11.0};\n                          Server=COCE-DS-LSTNR,50222;\n                          Database=Data_Reporting;\n                          trusted_connection=yes;")
```




#import data from query
```{r}
nofafsa_df <- dbGetQuery(
  conn = con_data_reporting, 
  statement = read_file(
    file = here::here("sql","no_fafsa_dialer_task_ug_21EW4.sql")
  )
) %>% as_tibble()
```



#import data from query - REPOPPED
```{r}
nofafsa_df_repop <- dbGetQuery(
  conn = con_data_reporting, 
  statement = read_file(
    file = here::here("sql","no_fafsa_dialer_task_ug_21EW4_repop.sql")
  )
) %>% as_tibble()
```



#import fafsa and file complete dates
```{r}
fafsa_dates_df <- dbGetQuery(
  conn = con_data_reporting, 
  statement = read_file(
    file = here::here("sql","FAFSA Dates.sql")
  )
) %>% as_tibble()
```


#database connection 50333
```{r connection-string,include=FALSE}
#database connection
con_data_reporting <- dbConnect(odbc::odbc(), .connection_string = "Driver={SQL Server Native Client 11.0};\n                          Server=COCE-LSTNR,50333;\n                          Database=AARDW;\n                          trusted_connection=yes;")
```



#importing Unify IDs from call logs if they were dialed in no fafsa dialer
```{r}
call_logs <- dbGetQuery(
  conn = con_data_reporting, 
  statement = read_file(
    file = here::here("sql","call_logs.sql")
  )
) %>% as_tibble()
```




# joining call logs to 50222 data
```{r}
nofafsa_df_calls <-
  as_tibble() %>%
  left_join(x = nofafsa_df,
          y = call_logs,
          by = c("ContactID" = "UnifySalesforceContactID")) 
#%>% 
  #filter(UnifySalesforceContactID != "Unknown")
  
```



#import dates table
```{r}
dates_df <- dbGetQuery(
  conn = con_aardw, 
  statement = read_file(
    file = here::here("sql","dates.sql")
  )
) %>% as_tibble()
```


#join to date table - FAFSA File Date
```{r}
fafsa_weekly_file_df <-
  as_tibble() %>%
  inner_join(x = fafsa_dates_df,
            y = dates_df,
            by = c("StudentFAFSAFileDate" = "DateFull")) 
```



#join to no fafsa results
```{r}
no_fafsa_weekly_file_df <-
  as_tibble() %>%
  left_join(x = fafsa_weekly_file_df,
            y = nofafsa_df_calls,
            by = c("ContactId" = "ContactID")) 
```

```{r}
write.csv(nofafsa_df_calls, "C:\\Users\\k.west2\\Desktop\\ug_dialer_min3.csv", row.names = FALSE)
```

#using original test population assignments with call and task data
```{r}
nofafsa_results <- 
  nofafsa_df_calls %>% 
  #filter(fafsa_completed==0) %>% 
  group_by(testing_group) %>% 
  summarise(
      InPopulation = n(), 
      `Funding Tasks` = sum(funding_task),
      `Funding %` = sum(funding_task)/n(),
      `Dialer Tasks` = sum(dialer_task),
      `Dialer Task %` = sum(dialer_task)/n(),
      Dialed = sum(dialed, na.rm=T),
      `Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Test Group` = testing_group) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       `Dialer Task %`,
       `Funding %`,
       `Dialed %`,
      `FAFSA Completion Rate`,
      `Reg Rate`,
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    `Funding Tasks`,
    `Dialer Tasks`,
    Dialed,
     #Apps
     `FAFSA Completed`,
    Regs,
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/2/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_results
  
```



#original test results (no call data)
```{r}
nofafsa_results <- 
  nofafsa_df %>% 
  #filter(!is.na(treatment)) %>% 
  group_by(testing_group) %>% 
  summarise(
      InPopulation = n(), 
      #`Funding Tasks` = sum(funding_task),
      #`Funding %` = sum(funding_task)/n(),
      #`Dialer Tasks` = sum(dialer_task),
      #`Dialer Task %` = sum(dialer_task)/n(),
      #Dialed = sum(dialed, na.rm=T),
      #`Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Test Group` = testing_group) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       #`Dialer Task %`,
       #`Funding %`,
       #`Dialed %`,
      `FAFSA Completion Rate`,
      `Reg Rate`,
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    #`Funding Tasks`,
    #`Dialer Tasks`,
    #Dialed,
     #Apps
     `FAFSA Completed`,
    Regs,
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control"),
    ) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/12/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_results 
  
```


```{r}
# Overall results save
nofafsa_results %>% gtsave(filename = "nofafsa_21EW4_overall_20210312_orgpop.png", path = here::here("imgs"))
```


#repopped
```{r}
nofafsa_repop_results <- 
  nofafsa_df_repop %>% 
  filter(!is.na(treatment)) %>% 
  group_by(treatment, new_test_or_control) %>% 
  summarise(
      InPopulation = n(), 
      #`Funding Tasks` = sum(funding_task),
      #`Funding %` = sum(funding_task)/n(),
      #`Dialer Tasks` = sum(dialer_task),
      #`Dialer Task %` = sum(dialer_task)/n(),
      #Dialed = sum(dialed, na.rm=T),
      #`Dialed %` = sum(dialed, na.rm=T)/n(),
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       #Enrolls = sum(Enrolls),
      #`Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  rename(`Treatment` = new_test_or_control) %>% 
 gt() %>%
     fmt_percent(columns = vars(
       #`Dialer Task %`,
       #`Funding %`,
       #`Dialed %`,
      `FAFSA Completion Rate`,
      `Reg Rate`,
      #`Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
    #`Funding Tasks`,
    #`Dialer Tasks`,
    #Dialed,
     #Apps
     `FAFSA Completed`,
    Regs,
    #Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/8/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


nofafsa_repop_results 
  
```


```{r}
# Overall results save
nofafsa_repop_results %>% gtsave(filename = "nofafsa_21EW4_overall_20210308_repop.png", path = here::here("imgs"))
```




```{r}
fafsa_weekly_file_results <- 
  no_fafsa_weekly_file_df %>% 
  filter(is.na(fafsa_completed)) %>% 
  group_by(WeekStartDate) %>% 
  summarise(
      InPopulation = n(), 
      `FAFSA Completed` = sum(fafsa_completed),
      `FAFSA Completion Rate` = sum(fafsa_completed)/n(),
      #Apps = sum(Apps),
       #`App Rate` = sum(Apps) / n(),
       Regs = sum(Regs),
      `Reg Rate` = sum(Regs) / n(),
       Enrolls = sum(Enrolls),
      `Enroll Rate` = sum(Enrolls) / n()
      #`FAFSA to Enroll Rate` = sum(Regs) / sum(fafsa_completed),
       #`App to Enroll` = sum(Regs) /sum(Apps) 
  ) %>% 
  #rename(`Test Group` = testing_group) %>% 
 gt() %>%
     fmt_percent(columns = vars(
      `FAFSA Completion Rate`,
      `Reg Rate`,
      `Enroll Rate`,
      #`FAFSA to Enroll Rate`,
      #`App to Enroll`
     ), decimals = 1) %>%
     fmt_number(columns = vars(
     #Leads,
    InPopulation,
     #Apps
     `FAFSA Completed`,
    Regs,
    Enrolls
     ), decimals = 0) %>%
      data_color(columns = vars(`FAFSA Completion Rate`), colors = "lightblue") %>%
   tab_header(
    title = md("21EW4 No FAFSA Dialing & Tasks: Test vs. Control")) %>% 
    tab_source_note(
    source_note = c("Data Source:  Unify Opportunity, SSR - retrieved on 3/1/21"))
  #%>%
     #data_color(columns = vars(`Melt Rate`), colors = "lightgreen") %>%
    #tab_options(
      # column_labels.font.size = 13,
      # table.font.size = 12
    #)


fafsa_weekly_file_results
  
```





